### 2017-12-30 icde/revision/Response.tex

\textbf{[R3W1\&D2]} \emph{More examples are suggested, especially when introducing the definitions, to make it easier for readers to understand.}

Yes, we agree that more examples (especially on how to generate components from scholarly data) will make our paper easier to understand. Due to the space limitation, we choose to add the examples in the extended version.

\textbf{[R3W2\&D4]} \emph{The memory cost of the algorithms is better to be reported in the experiments.}

We have reported the memory costs in a new set of experiments, \ie Exp-4 (page 10). 
On the large \aminer and \magdata, algorithm \pagerank uses the least memory, followed by algorithms \futurerank, \ensemblerank and \hhgrank, respectively.
%
The memory used by \pagerank is even less than the size of the academic graph data as it is based on the citation graph only.
%
Our \ensemblerank model costs more memory than \futurerank since it also combines article-venue relationships ignored by \futurerank and it assembles multiple rankings based on prestige and popularity. However, our \ensemblerank model is still more memory-efficient than \hhgrank.
%
To conclude, the \ensemblerank model uses reasonable amount of  memory to achieve the better effectiveness.

%that on the largest \magdata, (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB memory when $Y_s=2014$. Interestingly, our \ensemblerank model costs more memory than \futurerank due to its model complexity, while it is more efficient with our batch and incremental algorithms. seperate exp, between two baselines, author citation graph
%the memory cost of (\pagerank, \futurerank, \ensemblerank) is (12.65GB, 16.42GB, 49.42GB) when $Y_s=2015$, and the one of \hhgrank is 61.37GB when $Y_s=2014$.

### 2017-12-30 icde/revision/sec-exp.tex

In this section, we present an extensive experimental study of our approach \ensemblerank, compared with three competitive methods.
Using three real-life scholarly datasets (\aan, \aminer and \magdata) and two sets of ground-truth (\recom and \fcita), we conducted four sets of experiments to evaluate: (1) the effectiveness of \ensemblerank,
%two sets of benchmark article pairs (\recom and \fcita) ranked by numbers of recommendations and future citations,
(2) the efficiency of our batch algorithm \batensemble and incremental algorithm \incensemble, and (3) the impacts of parameters. %\ie time decaying factor $\sigma$, importance weighting factor $\lambda$ and aggregating parameters $\alpha$ and $\beta$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\graphscaleexpapp}{0.25}
\newcommand{\graphmarginexpapp}{3ex}
%%% all in 1 Figure
\begin{figure*}[tb!]
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-recm.eps}}
%\quad\quad
\hspace{\graphmarginexpapp}
%\hfill
\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-recm.eps}}
%\quad\quad
\hspace{\graphmarginexpapp}
%\hfill
\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-recm.eps}}
\\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2ex}
%\hspace{-10ex}
\subfigure[{\scriptsize \aan  with \fcita}]{\label{exp-aan-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-fcita.eps}}
%\quad\quad
\hspace{\graphmarginexpapp}
%\hfill
\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-fcita.eps}}
%\quad\quad
\hspace{\graphmarginexpapp}
%\hfill
\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-fcita.eps}}
\end{center}
\vspace{-1.5ex}
\caption{\small Accuracy evaluation: varying aggregating parameters $\alpha$ and $\beta$}
\label{exp-ab}
\vspace{-2ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t!]
%\vspace{-2ex}
\label{tab-result}
\begin{center}
\caption{\small Memory cost of algorithms}
%\begin{small}
\vspace{-.5ex}
\begin{tabular}{|c|c|c|c|c|}
\hline
{\bf Datasets}   &  \hspace{1ex}\pagerank\hspace{1ex}     & \hspace{1ex}\futurerank\hspace{1ex}  &  \hspace{1ex}\hhgrank\hspace{1ex}  &   \hspace{1ex}\ensemblerank\hspace{1ex}    \\
\hline \hline
\aan  & $0.671$   & $0.738$   & $0.758$     & {\bf 0.805}      \\  %\hline
\aminer  & $0.651$   & $0.729$   & $0.730$     & {\bf 0.778}      \\ %\hline
\magdata  & $0.615$   & $0.655$   & $0.658$     & {\bf 0.680}      \\ \hline
\end{tabular}
%\vspace{-.5ex}
%\end{small}
\end{center}
\vspace{-6ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

\stitle{Exp-4: Memory cost}.
In the fourth set of tests, we evaluated the memory cost of our algorithm. For a fair comparison, all algorithms used data before 2014, since the \hhgrank will run out of memory in 2015. The results of memory cost are reported in Table~IV.
The original data including
\markedb{The memory cost is an important factor of efficiency. We thus collect the memory use on the largest \magdata that (\futurerank, \ensemblerank) cost (16.42GB, 49.42GB) memory when $Y_s=2015$, and \hhgrank costs 61.37GB when $Y_s=2014$. Interestingly, our \ensemblerank model costs more memory than \futurerank due to its model complexity, while it is more efficient with our batch and incremental algorithms.}

>>>>

In this section, we present an extensive experimental study of our approach \ensemblerank, compared with three competitive methods.
Using three real-life scholarly datasets (\aan, \aminer and \magdata) and two sets of ground-truth (\recom and \fcita), we conducted five sets of experiments to evaluate: (1) the effectiveness of \ensemblerank,
%two sets of benchmark article pairs (\recom and \fcita) ranked by numbers of recommendations and future citations,
(2) the efficiency of our batch algorithm \batensemble and incremental algorithm \incensemble, (3) the memory cost, and (4) the impacts of parameters. %\ie time decaying factor $\sigma$, importance weighting factor $\lambda$ and aggregating parameters $\alpha$ and $\beta$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\graphscaleexpapp}{0.25}
\newcommand{\graphmarginexpapp}{3ex}
%%% all in 1 Figure
\begin{figure*}[tb!]
\addtolength{\subfigcapskip}{-1ex}
\begin{center}
\subfigure[{\scriptsize \aan with \recom}]{\label{exp-aan-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-recm.eps}}
%\quad\quad
\hspace{\graphmarginexpapp}
%\hfill
\subfigure[{\scriptsize \aminer with \recom}]{\label{exp-aminer-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-recm.eps}}
%\quad\quad
\hspace{\graphmarginexpapp}
%\hfill
\subfigure[{\scriptsize \magdata with \recom}]{\label{exp-mag-ab-recom}
\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-recm.eps}}
\\ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-2ex}
%\hspace{-10ex}
\subfigure[{\scriptsize \aan  with \fcita}]{\label{exp-aan-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/AAN-para-fcita.eps}}
%\quad\quad
\hspace{\graphmarginexpapp}
%\hfill
\subfigure[{\scriptsize \aminer with \fcita}]{\label{exp-aminer-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/AMiner-para-fcita.eps}}
%\quad\quad
\hspace{\graphmarginexpapp}
%\hfill
\subfigure[{\scriptsize \magdata with \fcita}]{\label{exp-mag-ab-fcita}
\includegraphics[scale=\graphscaleexpapp]{./exp/MAG-para-fcita.eps}}
\end{center}
\vspace{-1.5ex}
\caption{\small Accuracy evaluation: varying aggregating parameters $\alpha$ and $\beta$}
\label{exp-ab}
\vspace{-3ex}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t!]
%\vspace{-2ex}
\label{tab-result}
\begin{center}
\caption{\small Memory costs on \aminer and \magdata}
%\begin{small}
\vspace{-.5ex}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
{\bf Datasets}   &  Data     &  \pagerank     & \futurerank  &  \hhgrank  &   \ensemblerank    \\
\hline \hline
%\aan  & 6.80MB   & 5.03MB   & 5.86MB   & 11.06MB     & 13.09MB      \\  %\hline
%\aminer  & 288.87MB   & 263.81MB   & 404.46MB   & 1.34GB     & 1.28GB      \\ %\hline
%\magdata  & 10.46GB   & 8.67GB   & 14.32GB   & 61.37GB     & 48.13GB      \\ \hline
%\aan  & 6.8MB   & 5.03MB   & 5.86MB   & 11.06MB     & 13.09MB      \\  %\hline
\aminer  & 289MB   & 264MB   & 404MB   & 1.34GB     & 1.28GB      \\ %\hline
\magdata  & 10.5GB   & 8.7GB   & 14.3GB   & 61.4GB     & 48.1GB      \\ \hline
\end{tabular}
%\vspace{-.5ex}
%\end{small}
\end{center}
\vspace{-6ex}
\end{table}
%%%%%%%%%%%%%%%%%%%

\stitle{Exp-4: Memory cost}.
%
In the fourth set of tests, we evaluated the memory cost of our algorithm on the large \aminer and \magdata. For a fair comparison, we used all data on \aminer and data before 2014 on \magdata such that \hhgrank can finish the test. The results are reported in Table~IV, where the Data column records the size of the academic graph data, \ie the citation graph, author-article relationships, article-venue relationships and time information of articles.

On both datasets, algorithm \pagerank uses the least memory, followed by algorithms \futurerank, \ensemblerank and \hhgrank, respectively. 
%
The memory used by \pagerank is even less than the size of data as it is based on the citation graph only.
%
Our \ensemblerank model costs more memory than \futurerank since it also combines article-venue relationships ignored by \futurerank and it assembles multiple rankings based on prestige and popularity. However, our \ensemblerank model is still more memory-efficient than \hhgrank. 
%
To conclude, the \ensemblerank model uses reasonable amount of  memory to achieve the better effectiveness.

%For all algorithms, the memory cost increases with the original graph. Moreover, the more complexity the algorithm is, the more memory it costs. The memory cost of \pagerank is much lower than the one of other algorithms, since it only uses the citation information alone. Moreover, \ensemblerank costs more memory than \futurerank due to it also uses venue information besides of author information which \futurerank uses. The memory cost of \hhgrank is much higher than the one of other algorithms except on \aan possibly because the hypernetwork it generates will be more complicated with bigger original graph. Consider that, we choose to evaluate the prestige of an author with the average prestige of all articles published by the author instead of constructing an author citation graph with author component.

### 2017-12-30 icde/revision/sec-incAlg.tex

Our incremental algorithm \incensemble incrementally computes the popularity and prestige of associate entities.
We consider that an update $\Delta$ = $\Delta V\cup\Delta E$ is added to a (citation or venue) graph $G(V, E)$,
and the resulting graph is $G^+(V\cup\Delta V, E\cup\Delta E)$, where
$\Delta V$ is a set of nodes with $\Delta V\cap V = \emptyset$, and $\Delta E$ is a set of directed edges on $\Delta V$ and from $\Delta V$ to $V$ only, as citation relationships obey a natural temporal order, \ie an article only cites those published earlier, and it is rare for the mutual citations between two articles published in the same time.

>>>>

Our incremental algorithm \incensemble incrementally computes the popularity and prestige of associate entities.
We consider that an update $\Delta$ = $\Delta V\cup\Delta E$ is added to a (citation or venue) graph $G(V, E)$,
and the resulting graph is $G^+(V\cup\Delta V, E\cup\Delta E)$, where
$\Delta V$ is a set of nodes with $\Delta V\cap V = \emptyset$, and $\Delta E$ is a set of directed edges on $\Delta V$ and from $\Delta V$ to $V$ only, as citations obey a natural temporal order, \ie an article only cites those published earlier. %, and it is rare for the mutual citations between two articles published in the same time.
